\LARGE \bf Detection of design pattern : A systematic mapping study

### 2016-01-02 article/main.tex
modified:   main.tex

Design partterns are best pratices to recurring design problems first proposed
by the Gang of Four in their seminal book.

(Some study author) have been able to show that the presence of design patterns,
if correctly presented, can help developpers better understand a piece of
software [citation needed].
It would therefore be desirable to be able to automatically extract those
design patterns and present them in a digestible format.

Detection of design patterns in software has been a relatively active research
interest of the past decade in software engineering.
Proposed methods of automatic detection aims in part to facilitate the work of
developers in understanding a piece of software through reverse engineering.

@@

@@

For the classification phase, we distributed the 94 articles evenly among the
three evaluators.
Each article has been read thoroughly and classified according to the
classification scheme if considered relevant to the study.

Misleading articles that passed screening phase were removed at that point.
A total of 39 articles have been rejected in this fashion.

@@

\subsection{Publication type distribution}
\begin{figure}
  \centering
  \includegraphics[scale=0.40]{doctype.png}
  \caption{Distribution of papers by type of document}
\end{figure}

% Need a graphic for article by publishers.

@@

\bibitem{c2} www.scopus.com

\bibitem{c3} Landis, J. Richard, and Gary G. Koch. "The measurement of observer agreement for categorical data." biometrics (1977): 159-174.

>>>>

Design patterns are best practices to recurring design problems, first it was proposed by the Gang of Four in their seminal book.

(Some study author) have been able to show that the presence of design patterns,
if correctly presented, can help developers better understand a piece of
software [citation needed].
It would therefore be desirable to be able to automatically extract those
design patterns and present them in a digestible format.

Detection of design patterns in software has been a relatively active research
interest of the past decade in software engineering.
Proposed methods of automatic detection aims in part to facilitate the work of
developers in understanding a piece of software through reverse engineering and facilitate work during maintenance.

@@

Systematic mapping is a relatively new research method in software
engineering, adapted from other disciplines by Kitchenham
[5]. It is an alternative to systematic reviews and could be used if
the amount of empirical evidence is too little, or if the topic is too
broad, for a systematic review to be feasible. A mapping study is performed
at a higher granularity level with the aim to identify research
gaps and clusters of evidence in order to direct future research.
Petersen et al. [1] describe how to conduct
a systematic mapping study in software engineering. Our study
is conducted in accordance with these guidelines and 
we have introduced a classification scheme specific to our topic.

@@

@@

@@

\bibitem{c2} Landis, J. Richard, and Gary G. Koch. "The measurement of observer agreement for categorical data." biometrics (1977): 159-174.

\bibitem{C3} D. Yu, Y. Zhang and Z. Chen. "A comprehensive approach to the recovery of design pattern instances based on sub-patterns and method signatures" 2015, Journal of Systems and Software

\bibitem{C4} O. Kaczor, Y. Guéhéneuc and S. Hamel "Identification of design motifs with pattern matching algorithms" 2010, Information and Software Technology

\bibitem{C5} B.A. Kitchenham, Guidelines for performing systematic literature reviews in
software engineering version 2.3, Technical Report S.o.C.S.a.M. Software
Engineering Group, Keele University and Department of Computer Science
University of Durham, 2007.

\bibitem{C6} Tsantalis, N. Chatzigeorgiou, A. Stephanides, G. 
Halkidis, S.T., "Design pattern detection using similarity scoring" 2006, IEEE Transactions on Software Engineering

\bibitem{C7}

\bibitem{c3} www.scopus.com
